Proposed Solution

### 2017-01-24 CAV17/secs/postanal.tex
update notation

VeriConf can output the set of learned rules from the training set as
described in $\S$\ref{sec-learn}, recalling that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is sufficient for VeriConf to perform its core task of
configuration file validation, but can be used for more than 
simple rule checking. By re-interpreting
rules as being the edges of a {\bf Rule Graph}, we use tools from network
theory to extract information
about the configuration space. We inspect properties of the Rule Graph 
to triage reported errors by those most likely to be valid,
and even to estimate the complexity of configuration settings.

Accessibility of the Rule Graph is a hallmark of the association rule
learning technique applied by VeriConf \cite{someOtherGraphStuff}.
In contrast, the model output from a neural network is not as easily 
amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
to build on the work of previously developed methods and tools.

@@

We formally define the {\bf Rule Graph} as a directed hypergraph 
$H = (V,E)$ with labeled, weighted edges such that:

    $$V = \{ keywords \}$$

and

    $$E = \{ (V_s, V_t, l, w) \}$$

Where $V_s$ and $V_t$ are sets of vertices. Intuitively, we may think
of each ``hyperedge'' as being directed from $V_s$ to $V_t$. 
The label $l \in L$ indicates the predicate $p$ extracted by the learner,
where $L$ is the set of all predicates learned. 
The weight $w$ is defined as:

    $$w = \frac{true}{total}$$

as measured by the learner for that relationship.

We will also denote $E_{V_1, V_2} \subset E$ as the ``slice set'' of $E$ over $V_1, V_2$:

@@

We note that support and confidence assertions in the learner ensure
that all weights in the Rule Graph are positive.

\para {Definition}
We define a measure of degree for each node as the sum of in-degree
and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:

    $$DEGREE(x) = OUT\_DEGREE(x) + IN\_DEGREE(x)$$

    $$DEGREE(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$

@@

The more rules of high confidence are extracted for a keyword by the learner, 
the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
By classifying keywords in this way, we may extract a simple way to
order the {\it errors} reported by VeriConf by estimated importance.

We hypothesize that keywords (specifically their corresponding vertices)
of low $DEGREE$ will be rarer configuration
parameters where rules learned are more likely to be governed by 
tehchnical necessity, rather than industry convention. As such, errors
reported involving low-degree keywords are more likely to be errors
of high significance and should be presented with high importance
to users of VeriConf.

Specifically, for an error reported by VeriConf on a rule $r$ involving
keywords $K$, we may rank the errors simply by:

@@

We may also use the Rule Graph to advance our general knowledge
of the configuration space, outside the strict confines of a
verification system. As an example, we briefly present a heuristic
for configuration file complexity based on the topology of the
Rule Graph. This measure of complexity could be used by software
organizations to manage configuration files in much the same way
as Kolomogrov complexity is used to manage code - identifying
potentially brittle configurations for targeted refactoring.

@@

\begin{equation}
    COMPLEXITY(K, H) = \sum_{k \in K} \
        \begin{cases}
            1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|}) & \text{if}\ \ |E_{k, V}| > 0 \\
            1 & \text{otherwise}
        \end{cases}
\end{equation}

@@

The $COMPLEXITY$ measure can be thought of as an
extension of the na\"ive line-counting measure of complexity.
When a keyword in the configuration file is present in the Rule Graph,
we may consider the set $E_{k, K}$ to be all learned rules involving
keyword $k$ that
are {\it relevant} to the configuration file being examined. the set
$E_{k, V}$ denotes {\it all} learned rules involving $k$.
Given these sets, we may think of $\frac{|E_{k, K}|}{|E_{k, V}|}$
as representing the amount that $k$ is constrained in the current
configuration file relative to how much it could be constrained
in the global configuration space. The more constrained a configuration
keyword in a particular configuration file, the {\it less} it should
contribute to the complexity (hence $1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|})$).

>>>>

\app can output the set of learned rules from the training set as
described in $\S$\ref{sec-learn}, recalling that a rule is 
an implication relationship of the form $r = X \implies p(X,Y)$.
This data is sufficient for \app to perform its core task of
configuration file validation, but can be used for more than 
simple rule checking. By re-interpreting
rules as being the edges of a {\bf Rule Graph}, we use tools from network
theory to extract information
about the configuration space. We inspect properties of the Rule Graph 
to triage reported errors by those most likely to be valid,
and even to estimate the complexity of configuration settings.

Accessibility of the Rule Graph is a hallmark of the association rule
learning technique applied by \app \cite{someOtherGraphStuff}.
In contrast, the model output from a neural network is not as easily 
amenable to analysis \cite{nnAnalysis1, nnAnalysis2}, making it harder
to build on the work of previously developed methods and tools.

@@

We define the \textit{Rule Graph} as a directed hypergraph $H = (V,E)$,
   with vertices $V = \{ keywords \}$ and labeled, weighted edges $E = \{ (V_s, V_t, l, w) \}$.
The set of edges is constructed from the learned rules, using the keyword sets as source and targets, the predicates as labels, and the confidence as weights:

\begin{align*}
\forall r \in & Learn(\trainingSet).\ \exists e\ \in E.\\
              & V_s = X_r \land V_t=Y_r \land l=p_r \land w = confidence(r)
\end{align*}

We will also denote $E_{V_1, V_2} \subset E$ as the \textit{slice set} of $E$ over $V_1, V_2$:

@@

The use of the support and confidence thresholds $t_s$ and $t_c$ in the learner ensure 
that all weights in the Rule Graph are positive.

\para {Definition}
We define a measure of degree $\mathcal{D}(v)$ for each vertex $v$ as the sum of in-degree
and out-degree defined in the usual way. Explicitly, for a vertex $x \in V$:

    $$\mathcal{D}(x) = \sum_{v \in V} |E_{x, v}| + \sum_{v \in V} |E_{v, x}|$$

@@

The more rules of high confidence are extracted for a keyword by the learner, 
the higher the $DEGREE$ of the corresponding vertex in the Rule Graph.
By classifying keywords in this way, we may extract a simple way to
order the {\it errors} reported by \app by estimated importance.

We hypothesize that keywords (specifically their corresponding vertices)
of low $DEGREE$ will be rarer configuration
parameters where rules learned are more likely to be governed by 
tehchnical necessity, rather than industry convention. As such, errors
reported involving low-degree keywords are more likely to be errors
of high significance and should be presented with high importance
to users of \app.

Specifically, for an error reported by \app on a rule $r$ involving
keywords $K$, we may rank the errors simply by:

@@

We may also use the Rule Graph to advance our general knowledge
of the configuration space, outside the strict confines of a
verification system. As an example, we briefly present a heuristic
for configuration file complexity based on the topology of the
Rule Graph. This measure of complexity could be used by software
organizations to manage configuration files in much the same way
as Kolomogrov complexity~\cite{kolomogrov} is used to manage code - identifying
potentially brittle configurations for targeted refactoring.

@@

\begin{equation}
    \mathcal{C}(K, H) = \sum_{k \in K} \
        \begin{cases}
            1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|}) & \text{if}\ \ |E_{k, V}| > 0 \\
            1 & \text{otherwise}
        \end{cases}
\end{equation}

@@

The complexity measure, $\mathcal{C}$, can be thought of as an
extension of the na\"ive line-counting measure of complexity.
When a keyword in the configuration file is present in the Rule Graph,
we may consider the set $E_{k, K}$ to be all learned rules involving
keyword $k$ that
are {\it relevant} to the configuration file being examined. the set
$E_{k, V}$ denotes {\it all} learned rules involving $k$.
Given these sets, we may think of $\frac{|E_{k, K}|}{|E_{k, V}|}$
as representing the amount that $k$ is constrained in the current
configuration file relative to how much it could be constrained
in the global configuration space. The more constrained a configuration
keyword in a particular configuration file, the {\it less} it should
contribute to the complexity (hence $1 * (1 - \frac{|E_{k, K}|}{|E_{k, V}|})$).
